---
title: "Publication"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
## loading in datasets 
library(readr)
Sleep <- read_delim("/Users/emmaberg/Documents/2022/Research Project/Data/Datasets/Excel_TotalScore1/Sleep/sleep.txt",
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
View(Sleep)

library(readr)
Demo <- read_delim("/Users/emmaberg/Documents/2022/Research Project/Data/Datasets/Excel_TotalScore1/Demographics/demo.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
View(Demo)

library(readr)
Screen <- read_delim("/Users/emmaberg/Documents/2022/Research Project/Data/Datasets/Excel_TotalScore1/ScreenTime/screen.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
View(Screen)

library(readr)
Cog <- read_delim("/Users/emmaberg/Documents/2022/Research Project/Data/Datasets/Excel_TotalScore1/Cognition/cognition.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
View(Cog)

library(readr)
BaselineActivity <- read_delim("/Users/emmaberg/Documents/2022/Research Project/Data/Datasets/Excel_TotalScore1/Activities/Baseline/abcd_saiq02.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
View(BaselineActivity)

Fam <- read_delim("/Users/emmaberg/Documents/2022/Research Project/Data/Datasets/Excel_TotalScore1/Demographics/fam1.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
View(Fam)

Site <- read_delim("/Users/emmaberg/Documents/2022/Research Project/Data/Datasets/Excel_TotalScore1/Demographics/site1.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
View(Site)

BrainData <- read_delim("/Users/emmaberg/Documents/2022/Research Project/Data/Datasets/Excel_TotalScore1/braindata1.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
View(BrainData)

length(unique(BaselineActivity$src_subject_id)) 
#11876
length(unique(Cog$src_subject_id)) 
#11876
length(unique(Screen$src_subject_id))
#11876
length(unique(Demo$src_subject_id))
#11876
length(unique(Sleep$src_subject_id))
#11876
length(unique(Fam$src_subject_id))
#11876
length(unique(Site$src_subject_id))
#11876
length(unique(Fam$src_subject_id))
#11876
length(unique(BrainData$src_subject_id))
#11811
```
## loading in libraries
```{r}
library(haven)
library(data.table)
library(JWileymisc)
library(ggplot2)
library(ggpubr)
library(visreg)
library(tidyverse)
library(psych)
```
# Convert to data tables
```{r}
library(data.table)
BaselineActivityTable <- as.data.table(BaselineActivity)
CogTable <- as.data.table(Cog)
DemoTable <- as.data.table(Demo)
ScreenTable <- as.data.table(Screen)
SleepTable <- as.data.table(Sleep)
FamTable <- as.data.table(Fam)
SiteTable <- as.data.table(Site)
BrainDataTable <- as.data.table(BrainData)

## getting rid of the timepoints that aren't in any other dataset

SiteReal <- SiteTable[eventname %in% c("1_year_follow_up_y_arm_1", "baseline_year_1_arm_1", "2_year_follow_up_y_arm_1", "3_year_follow_up_y_arm_1")]

SiteRealTable <- as.data.table(SiteReal)
```

## Merging

```{r}
## merging datasets by ID and time point

screensleep <- merge(
  x = ScreenTable,
  y = SleepTable,
  by = c('src_subject_id', 'eventname'),
  all = TRUE)

screensleep <- select(screensleep, 
                                       -c("collection_id.y",
                                          "dataset_id.y", "subjectkey.y", 
                                          "interview_date.y", "interview_age.y",
                                          "sex.y"))

screensleepcog <- merge(
  x = screensleep,
  y = CogTable,
  by = c('src_subject_id', 'eventname'),
  all = TRUE)

screensleepcog <- select(screensleepcog, 
                                       -c("collection_id",
                                          "dataset_id", "subjectkey", 
                                          "interview_date", "interview_age",
                                          "sex"))


screensleepcogdemo <- merge(
  x = screensleepcog,
  y = DemoTable,
  by = c('src_subject_id', 'eventname'),
  all = TRUE)

screensleepcogdemo <- select(screensleepcogdemo, 
                                       -c("collection_id",
                                          "dataset_id", "subjectkey", 
                                          "interview_date", "interview_age",
                                          "sex"))

screensleepcogdemoact <- merge(
  x = screensleepcogdemo,
  y = BaselineActivityTable,
  by = c('src_subject_id', 'eventname'),
  all = TRUE)

screensleepcogdemoact<- select(screensleepcogdemoact, 
                                       -c("collection_id",
                                          "dataset_id", "subjectkey", 
                                          "interview_date", "interview_age",
                                          "sex"))


sitefull <- merge(
  x = screensleepcogdemoact,
  y = SiteRealTable,
  by = c('src_subject_id', 'eventname'),
  all = TRUE)

sitefull <- select(sitefull, 
                                       -c("collection_id",
                                          "dataset_id", "subjectkey", 
                                          "interview_date", "interview_age",
                                          "sex"))

Sitefam <- merge(
  x = sitefull,
  y = FamTable,
  by = c('src_subject_id', 'eventname'),
  all = TRUE)


Sitefam <- select(Sitefam, 
                                       -c("collection_id",
                                          "dataset_id", "subjectkey", 
                                          "interview_date", "interview_age",
                                          "sex"))

Fulldata <-merge(
  x = Sitefam,
  y = BrainDataTable,
  by = c('src_subject_id', 'eventname'),
  all = TRUE)

Fulldata <- select(Fulldata, 
                                       -c("collection_id",
                                          "dataset_id", "subjectkey", 
                                          "interview_date", "interview_age",
                                          "sex"))



length(unique(Fulldata$src_subject_id))
#11876
as.data.table(Fulldata)
```
## Variable management 

## Cognition
```{r}
## crystallised
str(Fulldata$nihtbx_cryst_uncorrected)

## total
str(Fulldata$nihtbx_totalcomp_uncorrected)

## fluid

##flanker
str(Fulldata$nihtbx_flanker_uncorrected)

##picture
str(Fulldata$nihtbx_picture_uncorrected)

##pattern
str(Fulldata$nihtbx_pattern_uncorrected)

## baseline fluid
str(Fulldata$nihtbx_fluidcomp_uncorrected)
```

## Sleep total scores
```{r}

## sleep initiation (in minutes)
str(Fulldata$sleepdisturb1_p)

## sleep maintenence (how many hours asleep)
str(Fulldata$sleepdisturb2_p)

## total sleep score
str(Fulldata$sleep_total)
```

## Screen total scores
```{r}

## total weekday screen time
str(Fulldata$total_weekday)

## total weekend screen time
str(Fulldata$total_weekend)

## total screen time
totalscreentime <- Fulldata$total_weekday + Fulldata$total_weekend

Fulldata <- Fulldata %>%
  add_column(Column_After = totalscreentime,
             .after = "total_weekend") 

names(Fulldata)[names(Fulldata) == 'Column_After'] <- "total_screen"

hist(Fulldata$total_screen)

hist(log(Fulldata$total_screen))

## how often play mature-rated video games
str(Fulldata$screen13_y)

## how often watch r-rated movies
str(Fulldata$screen14_y)
```

## Activities total scores

```{r}

## how many sports activities in past 12 months
str(Fulldata$TotalSport)

## how many arts activities in past 12 months
str(Fulldata$TotalArt)

## how many sports+arts activities in past 12 months
str(Fulldata$TotalParticipation)
```

## Distributions

## Cognition
```{r}
hist(Fulldata$nihtbx_totalcomp_uncorrected)
hist(Fulldata$nihtbx_fluidcomp_uncorrected,
     main = "Histogram of FCF Composite Score",
     xlab = "FCF Composite Score")


describe(Fulldata$nihtbx_fluidcomp_uncorrected)

hist(Fulldata$nihtbx_cryst_uncorrected,
     main = "Histogram of CCF Composite Score",
     xlab = "CCF Composite Score")
## all appear normal

describe(Fulldata$nihtbx_cryst_uncorrected)


qqnorm(Fulldata$nihtbx_fluidcomp_uncorrected, pch = 1, frame = FALSE,
       main = "QQ plot of FCF composite score")
qqline(Fulldata$nihtbx_fluidcomp_uncorrected, col = "steelblue", lwd = 2)

qqnorm(Fulldata$nihtbx_cryst_uncorrected, pch = 1, frame = FALSE,
       main = "QQ plot of CCF composite score")
qqline(Fulldata$nihtbx_cryst_uncorrected, col = "steelblue", lwd = 2)

##flanker
hist(Fulldata$nihtbx_flanker_uncorrected,
     main = "Histogram of Flanker scores",
     xlab = "Flanker scores")

qqnorm(Fulldata$nihtbx_flanker_uncorrected, pch = 1, frame = FALSE,
       main = "QQ plot of Flanker scores")
qqline(Fulldata$nihtbx_flanker_uncorrected, col = "steelblue", lwd = 2)

#appears slightly left skewed
describe(Fulldata$nihtbx_flanker_uncorrected)
# skew = -0.98, kurtosis = 1.68. no need to transform.

##picture
hist(Fulldata$nihtbx_picture_uncorrected,
     main = "Histogram of Picture scores",
     xlab = "Picture scores")
#normal

qqnorm(Fulldata$nihtbx_picture_uncorrected, pch = 1, frame = FALSE,
       main = "QQ plot of Picture scores")
qqline(Fulldata$nihtbx_picture_uncorrected, col = "steelblue", lwd = 2)

describe(Fulldata$nihtbx_picture_uncorrected)


##pattern
hist(Fulldata$nihtbx_pattern_uncorrected,
    main = "Histogram of Pattern scores",
     xlab = "Pattern scores")
#normal

describe(Fulldata$nihtbx_pattern_uncorrected)


qqnorm(Fulldata$nihtbx_pattern_uncorrected, pch = 1, frame = FALSE,
       main = "QQ plot of Pattern scores")
qqline(Fulldata$nihtbx_pattern_uncorrected, col = "steelblue", lwd = 2)
```

## Sleep
```{r}

## Sleep Total Variable
hist(Fulldata$sleep_total)
## appears to be right skewed. Checking kurtosis and skew.
describe(Fulldata$sleep_total)
## skew = 1.8, kurtosis = 5.8
## applying transformation
logsleep_total <- log(Fulldata$sleep_total)
hist(logsleep_total)
## normal now

hist(Fulldata$sleepdisturb1_p,
     main = "Histogram of sleep duration variable",
     xlab = "Sleep duration (rated on Likert scale)")
# appears slightly right skewed 
# checking skew and kurtosis
describe(Fulldata$sleepdisturb1_p)
# skew = 0.82, kurtosis = 0.26. no need to transform.

qqnorm(Fulldata$sleepdisturb1_p, pch = 1, frame = FALSE,
       main = "QQ plot of sleep duration")
qqline(Fulldata$sleepdisturb1_p, col = "steelblue", lwd = 2)

qqnorm(Fulldata$sleepdisturb1_p, pch = 1, frame = FALSE)
qqline(Fulldata$sleepdisturb1_p, col = "steelblue", lwd = 2)

hist(Fulldata$sleepdisturb2_p,
     main = "Histogram of sleep initiation variable",
     xlab = "Sleep initiation (rated on Likert scale)")
# appears slightly right skewed 
# checking skew and kurtosis
describe(Fulldata$sleepdisturb2_p)
# skew = 1.08, kurtosis = 0.8. no need to transform.


qqnorm(Fulldata$sleepdisturb2_p, pch = 1, frame = FALSE,
       main = "QQ plot of sleep initiation variable")
qqline(Fulldata$sleepdisturb2_p, col = "steelblue", lwd = 2)
```

## Screen Time
```{r}
hist(Fulldata$total_weekday, main= "Histogram of Weekday Screen Time", xlab= "Weekday Screen Time (Hours)",
     xlim=c(0,25), ylim=c(0,10000))

hist(Fulldata$total_weekday, xaxt = "n")
axis(side=1, at=seq(0,24, 4))

qqnorm(Fulldata$total_weekday, pch = 1, frame = FALSE,
       main = "QQ plot of weekday screen time")
qqline(Fulldata$total_weekday, col = "steelblue", lwd = 2)

## appears right skewed
## checking skew and kurtosis
describe(Fulldata$total_weekday)
# skew = 1.7, kurtosis = 3.77.

## applying log transformation
## adding constant
total_weekday1 <- Fulldata$total_weekday + 1
logtotal_weekday1 <- log(total_weekday1)
hist(logtotal_weekday1, 
     main = "Histogram of Log Weekday Screen Time",
     xlab = "Log Weekday Screen Time")
#normal now

qqnorm(Fulldata$total_weekday, pch = 1, frame = FALSE)
qqline(Fulldata$total_weekday, col = "steelblue", lwd = 2)

library("car")
qqPlot(Fulldata$total_weekday)

hist(Fulldata$total_weekend,
     main = "Histogram of Weekend Screen Time",
     xlab= "Weekend Screen Time (Hours)",
     xlim=c(0,25), ylim=c(0,8000))


qqnorm(Fulldata$total_weekend, pch = 1, frame = FALSE,
       main = "QQ plot of weekday screen time")
qqline(Fulldata$total_weekend, col = "steelblue", lwd = 2)

qqnorm(Fulldata$total_screen, pch = 1, frame = FALSE,
       main = "QQ plot of total screen time")
qqline(Fulldata$total_screen, col = "steelblue", lwd = 2)

# appears right skewed
# checking skew and kurtosis
describe(Fulldata$total_weekend)
# skew = 1.53, kurtosis = 3.06
# transforming
## adding constant
total_weekend1 <- Fulldata$total_weekend + 1
logtotal_weekend1 <- log(total_weekend1)
hist(logtotal_weekend1,
     main= "Histogram of Log Weekend Screen Time",
     xlab= "Log Weekend Screen Time")
## appears normal now

qqnorm(logtotal_weekend1, pch = 1, frame = FALSE)
qqline(logtotal_weekend1, col = "steelblue", lwd = 2)

##adding log transformed values to fulldata dataset

#totalweekend
library(tibble)
Fulldata <- Fulldata %>%
  add_column(Column_After = log(total_weekend1),
             .after = "total_weekend") 

names(Fulldata)[names(Fulldata) == 'Column_After'] <- "logtotal_weekend1"

#totalweekday
library(tibble)
Fulldata <- Fulldata %>%
  add_column(Column_After = log(total_weekday1),
             .after = "total_weekday") 

names(Fulldata)[names(Fulldata) == 'Column_After'] <- "logtotal_weekday1"

#totalscreentime
hist(Fulldata$total_screen,
     main= "Histogram of Total Screen Time",
     xlab="Total Screen Time (Hours)",
     xlim=c(0,50), ylim=c(0,10000))
# transforming
## adding constant
total_screen1 <- Fulldata$total_screen + 1
logtotal_screen1 <- log(total_screen1)
hist(logtotal_screen1,
     main ="Histogram of Log Total Screen Time",
     xlab="Log Total Screen Time",
     xlim=c(0,4), ylim=c(0,3000))
## appears normal now

describe(Fulldata$total_screen)
# adding log total screen to dataset
library(tibble)
Fulldata <- Fulldata %>%
  add_column(Column_After = log(total_screen1),
             .after = "total_screen") 

names(Fulldata)[names(Fulldata) == 'Column_After'] <- "logtotal_screen1"

hist(Fulldata$screen13_y)
## appears right skewed
## checking skew and kurtosis
describe(Fulldata$screen13_y)
# skew = 1.45, kurtosis = 1.19. 
# no need to transform

hist(Fulldata$screen14_y)
## appears right skewed
## checking skew and kurtosis
describe(Fulldata$screen14_y)
# skew = 1.79, kurtosis = 3.47. 
## applying log transformation
logscreen14_y <- log(Fulldata$screen14_y)
hist(logscreen14_y)
sqrtlog14_y <- sqrt(Fulldata$screen14_y)
hist(sqrtlog14_y)
# not changing much. leaving as is.
```
## Activities
```{r}
hist(Fulldata$TotalSport,
     main = "Histogram of sport activities",
     xlab = "Number of sport activities")

qqnorm(Fulldata$TotalSport, pch = 1, frame = FALSE,
       main = "QQ plot of sport activities")
qqline(Fulldata$TotalSport, col = "steelblue", lwd = 2)

## appears right skewed
# checking skew and kurtosis
describe(Fulldata$TotalSport)
# skew = 1.11, kurtosis = 1.76
# no need to transform

hist(Fulldata$TotalArt,
      main = "Histogram of arts activities",
     xlab = "Number of arts activities")
# appears normal

describe(Fulldata$TotalArt)

qqnorm(Fulldata$TotalArt, pch = 1, frame = FALSE,
       main = "QQ plot of arts activities")
qqline(Fulldata$TotalArt, col = "steelblue", lwd = 2)

hist(Fulldata$TotalParticipation,
     main = "Histogram of total activities",
     xlab = "Number of total activities")

describe(Fulldata$TotalParticipation)

qqnorm(Fulldata$TotalParticipation, pch = 1, frame = FALSE,
       main = "QQ plot of total activities")
qqline(Fulldata$TotalParticipation, col = "steelblue", lwd = 2)
# appears normal
```

## Checking number of observations at each timepoint
```{r}

## seeing how many people have baseline.
fdbl <- Fulldata[eventname == "baseline_year_1_arm_1"]
summary (fdbl)

## 11876 with baseline. what we expect which is good!

## seeing how many people have the one year follow up.
fdone <- Fulldata[eventname == "1_year_follow_up_y_arm_1"]
summary (fdone)

## 11225 have the one year follow up. 94.5%

## seeing how many people have the two year follow up.
fdtwo <- Fulldata[eventname == "2_year_follow_up_y_arm_1"]
summary (fdtwo)

## 10414 have the two year follow up. 87.7%

## seeing how many people have the three year follow up.

fdthree <- Fulldata[eventname == "3_year_follow_up_y_arm_1"]
summary (fdthree)

## 6251 people have three year follow up. 6251/11876 = 53% of participants have third timepoint.
```
## Randomly splitting data
```{r}
# Creating subset of data 

fdsubset <- Fulldata[eventname == "baseline_year_1_arm_1"]

as.data.table(fdsubset)
write.csv(fdsubset, "fdsubset.csv")

as.data.table(Fulldata)
write.csv(Fulldata, "Fulldata.csv")


# Split model dataset into 2 random subsamples:

fdsubset$subsample <- sample(factor(rep(1:2, length.out=nrow(fdsubset)), 
                                 labels=paste0("subsample", 1:2)))
FD_subsample1 <- fdsubset[which(fdsubset$subsample=="subsample1"), ]
FD_subsample2 <- fdsubset[which(fdsubset$subsample=="subsample2"), ]

# if Fulldata$src_subject_id is in FD_subample1, mark is as TRUE for var s1, same for var 2 with subsample2:

Fulldata$s1 <- Fulldata$src_subject_id %in% FD_subsample1$src_subject_id
Fulldata$s2 <- Fulldata$src_subject_id %in% FD_subsample2$src_subject_id

## below includes 3 year follow up so use for sensitivity analysis

Fulldata_s1 <- Fulldata[which(Fulldata$s1 == TRUE),]
Fulldata_s2 <- Fulldata[which(Fulldata$s2 == TRUE),]

# delete 3 year follow up from fulldatas1 and s2. run models on these.

Fulldata_s1_limited <- Fulldata_s1[!eventname == "3_year_follow_up_y_arm_1"]

length(unique(Fulldata_s1_limited$src_subject_id))
#5938
Fulldata_s2_limited <- Fulldata_s2[!eventname == "3_year_follow_up_y_arm_1"]
length(unique(Fulldata_s2_limited$src_subject_id))
#5938
```

## Libraries
```{r}
library(tufte)
library(haven)
library(data.table)
library(JWileymisc)
library(psych)
library(ggplot2)
library(ggpubr)
library(ggthemes)
library(scales)
library(ggExtra)
```
## Cronbach's alpha
```{r}
# Sleep
psych::alpha(as.data.frame(Sleep[c("sleepdisturb1_p", "sleepdisturb2_p", "sleepdisturb3_p", "sleepdisturb4_p", "sleepdisturb5_p", "sleepdisturb6_p", "sleepdisturb7_p", "sleepdisturb8_p", "sleepdisturb9_p", "sleepdisturb10_p", "sleepdisturb11_p","sleepdisturb12_p","sleepdisturb13_p","sleepdisturb14_p","sleepdisturb15_p","sleepdisturb16_p","sleepdisturb17_p","sleepdisturb18_p","sleepdisturb19_p", "sleepdisturb20_p", "sleepdisturb21_p","sleepdisturb22_p","sleepdisturb23_p","sleepdisturb24_p","sleepdisturb25_p","sleepdisturb26_p")]), check.keys=TRUE)

## Activities - sport
psych::alpha(as.data.frame(BaselineActivity[c("sai_p_dance_p12", "sai_p_base_p12", "sai_p_basket_p12", "sai_p_climb_p12", "sai_p_fball_p12", "sai_p_gym_p12", "sai_p_ihock_p12", "sai_p_polo_p12", "sai_p_iskate_p12", "sai_p_m_arts_p12", "sai_p_lax_p12","sai_p_sboard_p12___0", "sai_p_wpolo_p12", "sai_p_run_p12", "sai_p_mma_p12", "sai_p_vball_p12", "sai_p_yoga_p12", "sai_p_music_p12", "sai_p_art_p12", "sai_p_drama_p12", "sai_p_crafts_p12", "sai_p_chess_p12", "sai_p_collect_p12", "sai_p_lmusic","sai_p_read")]), check.keys=TRUE)

## Activites - art
psych::alpha(as.data.frame(BaselineActivity[c("sai_p_music_p12", "sai_p_art_p12", "sai_p_drama_p12", "sai_p_crafts_p12", "sai_p_chess_p12", "sai_p_collect_p12", "sai_p_lmusic","sai_p_read")]), check.keys=TRUE)

## Cognition - FCF
psych::alpha(as.data.frame(Cog[c("nihtbx_flanker_uncorrected", "nihtbx_picture_uncorrected", "nihtbx_pattern_uncorrected", "nihtbx_list_uncorrected", "nihtbx_cardsort_uncorrected", "nihtbx_reading_uncorrected", "nihtbx_picvocab_uncorrected")]), check.keys=TRUE)

## Screen
psych::alpha(as.data.frame(Screen[c("screen1_wkdy_y", "screen2_wkdy_y", "screen3_wkdy_y", "screen4_wkdy_y", "screen5_wkdy_y", "screen_wkdy_y", "screen9_wknd_y", "screen10_wknd_y", "screen11_wknd_y", "screen12_wknd_y")]), check.keys=TRUE)

```
## FCF trajectories over time - is t2 significantly different from t1?
```{r}
widedata <- reshape(
  data=Fulldata_s1_limited,
  timevar = "eventname",
  idvar = "src_subject_id",
  direction = "wide")

#Flanker
t.test(widedata$nihtbx_flanker_uncorrected.baseline_year_1_arm_1, widedata$nihtbx_flanker_uncorrected.2_year_follow_up_y_arm_1, paired = TRUE)


meanfbl <- mean(widedata$nihtbx_flanker_uncorrected.baseline_year_1_arm_1, na.rm = TRUE)
meanfbl
sd(widedata$nihtbx_flanker_uncorrected.baseline_year_1_arm_1, na.rm = TRUE)

meanf2 <- mean(widedata$nihtbx_flanker_uncorrected.2_year_follow_up_y_arm_, na.rm = TRUE)
sd(widedata$nihtbx_flanker_uncorrected.2_year_follow_up_y_arm_, na.rm = TRUE)

#Pattern
t.test(widedata$nihtbx_pattern_uncorrected.baseline_year_1_arm_1, widedata$nihtbx_pattern_uncorrected.2_year_follow_up_y_arm_1, paired = TRUE)

mean(widedata$nihtbx_pattern_uncorrected.baseline_year_1_arm_1, na.rm = TRUE)
sd(widedata$nihtbx_pattern_uncorrected.baseline_year_1_arm_1, na.rm = TRUE)

mean(widedata$nihtbx_pattern_uncorrected.2_year_follow_up_y_arm_, na.rm = TRUE)
sd(widedata$nihtbx_pattern_uncorrected.2_year_follow_up_y_arm_, na.rm = TRUE)


#Picture
t.test(widedata$nihtbx_picture_uncorrected.baseline_year_1_arm_1, widedata$nihtbx_picture_uncorrected.2_year_follow_up_y_arm_1, paired = TRUE)

mean(widedata$nihtbx_picture_uncorrected.baseline_year_1_arm_1, na.rm = TRUE)
sd(widedata$nihtbx_picture_uncorrected.baseline_year_1_arm_1, na.rm = TRUE)

mean(widedata$nihtbx_picture_uncorrected.2_year_follow_up_y_arm_, na.rm = TRUE)
sd(widedata$nihtbx_picture_uncorrected.2_year_follow_up_y_arm_, na.rm = TRUE)

# cryst composite
mean(widedata$nihtbx_cryst_uncorrected.baseline_year_1_arm_1, na.rm = TRUE)
sd(widedata$nihtbx_cryst_uncorrected.baseline_year_1_arm_1, na.rm = TRUE)

# fcf composite
mean(widedata$nihtbx_fluidcomp_uncorrected.baseline_year_1_arm_1, na.rm = TRUE)
sd(widedata$nihtbx_fluidcomp_uncorrected.baseline_year_1_arm_1, na.rm = TRUE)
```

## Descriptives
```{r}

BLsubset <- Fulldata[eventname == "baseline_year_1_arm_1"]

twoyearsubset <- Fulldata[eventname == "2_year_follow_up_y_arm_1"]

#mean number of sport activities
mean(BaselineActivity$TotalSport, na.rm=TRUE)
sd(BaselineActivity$TotalSport)

#mean number of arts activities
mean(BaselineActivity$TotalArt)
sd(BaselineActivity$TotalArt)

#mean sleep duration scores
mean(BLsubset$sleepdisturb1_p, na.rm=TRUE)

#mean sleep initiation scores
mean(BLsubset$sleepdisturb2_p)

#mean weekday screen time scores
mean(BLsubset$total_weekday, na.rm=TRUE)

sd(BLsubset$total_weekday, na.rm=TRUE)

#mean weekend screen time scores
mean(BLsubset$total_weekend, na.rm=TRUE)
sd(BLsubset$total_weekend, na.rm=TRUE)

```

## Bivariate correlations b/w modifiable factors 
```{r}

## Sleep duration and Activities
cor.test(Fulldata$sleepdisturb1_p, Fulldata$TotalParticipation, method="pearson")

## Sleep initiation and activities
cor.test(Fulldata$sleepdisturb2_p, Fulldata$TotalParticipation, method="pearson")

##Sleep duration and weekday screen
cor.test(Fulldata$sleepdisturb1_p,Fulldata$total_weekday, method="pearson")

## Sleep duration and weekend screen
cor.test(Fulldata$sleepdisturb1_p,Fulldata$total_weekend, method="pearson")

## Sleep initiation and weekday screen
cor.test(Fulldata$sleepdisturb2_p,Fulldata$total_weekday, method="pearson")

## Sleep initiation and weekend screen
cor.test(Fulldata$sleepdisturb2_p,Fulldata$total_weekend, method="pearson")

##Activities and weekday screen
cor.test(Fulldata$TotalParticipation,Fulldata$total_weekday, method="pearson")

##Activities and weekend screen
cor.test(Fulldata$TotalParticipation,Fulldata$total_weekend, method="pearson")

```
# Bivariate correlations using lm
```{r}

## Sleep duration
cor.test(Fulldata$sleepdisturb1_p, Fulldata$sleepdisturb2_p, method="pearson")

cor.test(Fulldata$sleepdisturb1_p, Fulldata$TotalArt, method="pearson")

cor.test(Fulldata$sleepdisturb1_p, Fulldata$TotalSport, method="pearson")

cor.test(Fulldata$sleepdisturb1_p, Fulldata$total_weekday, method="pearson")

cor.test(Fulldata$sleepdisturb1_p, Fulldata$total_weekend, method="pearson")

cor.test(Fulldata$sleepdisturb1_p, Fulldata$total_screen, method="pearson")

## Sleep initiation
cor.test(Fulldata$sleepdisturb2_p, Fulldata$sleepdisturb1_p, method="pearson")

cor.test(Fulldata$sleepdisturb2_p, Fulldata$TotalArt, method="pearson")

cor.test(Fulldata$sleepdisturb2_p, Fulldata$TotalSport, method="pearson")

cor.test(Fulldata$sleepdisturb2_p, Fulldata$total_weekday, method="pearson")

cor.test(Fulldata$sleepdisturb2_p, Fulldata$total_weekend, method="pearson")

cor.test(Fulldata$sleepdisturb2_p, Fulldata$total_screen, method="pearson")

## Art
cor.test(Fulldata$TotalArt, Fulldata$sleepdisturb1_p, method="pearson")

cor.test(Fulldata$TotalArt, Fulldata$sleepdisturb2_p, method="pearson")

cor.test(Fulldata$TotalArt, Fulldata$TotalSport, method="pearson")

cor.test(Fulldata$TotalArt, Fulldata$total_weekday, method="pearson")

cor.test(Fulldata$TotalArt, Fulldata$total_weekend, method="pearson")

cor.test(Fulldata$TotalArt, Fulldata$total_screen, method="pearson")

## Sport
cor.test(Fulldata$TotalSport, Fulldata$total_weekday, method="pearson")

cor.test(Fulldata$TotalSport, Fulldata$total_weekend, method="pearson")

cor.test(Fulldata$TotalSport, Fulldata$total_screen, method="pearson")

## Weekday
cor.test(Fulldata$total_weekday, Fulldata$total_weekend, method="pearson")

cor.test(Fulldata$total_weekday, Fulldata$total_screen, method="pearson")

## Weekend

cor.test(Fulldata$total_weekend, Fulldata$total_screen, method="pearson")

## total activiites
cor.test(Fulldata$TotalParticipation, Fulldata$sleepdisturb1_p, method="pearson")
cor.test(Fulldata$TotalParticipation, Fulldata$sleepdisturb2_p, method="pearson")
cor.test(Fulldata$TotalParticipation, Fulldata$total_weekday, method="pearson")
cor.test(Fulldata$TotalParticipation, Fulldata$total_weekend, method="pearson")
cor.test(Fulldata$TotalParticipation, Fulldata$total_screen, method="pearson")
```

## Models


#libraries
```{r}
library(lme4)
library(lmerTest)
library(lmtest)
```
# Hypothesis 1

## reshaping from long to wide so that I can run models with different timepoints
```{r}
widedata <- reshape(
  data=Fulldata_s1_limited,
  timevar = "eventname",
  idvar = "src_subject_id",
  direction = "wide")
```
# Hypothesis 1A - residual change models
## Model 4 - Sleep 
lm(FCFwavethree ~ sleepbaseline + FCFbaseline)
## Flanker
```{r}
## Model 4a - sleep duration and flanker
m4a <- lm(nihtbx_flanker_uncorrected.2_year_follow_up_y_arm_1 ~ sleepdisturb1_p.baseline_year_1_arm_1 + nihtbx_flanker_uncorrected.baseline_year_1_arm_1, data = widedata)

library(lm.beta)
summary(m4a)
confint(m4a)
lm.beta(m4a)


md4a <- modelDiagnostics(m4a, ev.perc = .005)
plot(md4a, ncol = 2, ask = FALSE)

## Model 4b - sleep initiation and flanker
m4b <- lm(nihtbx_flanker_uncorrected.2_year_follow_up_y_arm_1 ~ sleepdisturb2_p.baseline_year_1_arm_1 + nihtbx_flanker_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m4b)
confint(m4b)
lm.beta(m4b)

md4b <- modelDiagnostics(m4b, ev.perc = .005)
plot(md4b, ncol = 2, ask = FALSE)


## Model 4c - both and flanker
m4c <- lm(nihtbx_flanker_uncorrected.2_year_follow_up_y_arm_1 ~ sleepdisturb1_p.baseline_year_1_arm_1 + sleepdisturb2_p.baseline_year_1_arm_1 + nihtbx_flanker_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m4c)
```
## Pattern Comparison 
```{r}
## Model 4d - sleep duration and pattern

m4d <- lm(nihtbx_pattern_uncorrected.2_year_follow_up_y_arm_1 ~ sleepdisturb1_p.baseline_year_1_arm_1 + nihtbx_pattern_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m4d)
confint(m4d)
lm.beta(m4d)

md4d <- modelDiagnostics(m4d, ev.perc = .005)
plot(md4d, ncol = 2, ask = FALSE)

## Model 4e - sleep initiation and pattern

m4e <- lm(nihtbx_pattern_uncorrected.2_year_follow_up_y_arm_1 ~ sleepdisturb2_p.baseline_year_1_arm_1 + nihtbx_pattern_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m4e)
confint(m4e)
lm.beta(m4e)

md4e <- modelDiagnostics(m4e, ev.perc = .005)
plot(md4e, ncol = 2, ask = FALSE)

## Model 4f - both and pattern

m4f <- lm(nihtbx_pattern_uncorrected.2_year_follow_up_y_arm_1 ~ sleepdisturb1_p.baseline_year_1_arm_1 + sleepdisturb2_p.baseline_year_1_arm_1 + nihtbx_pattern_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m4f)

```
## Picture Sequence
```{r}
## Model 4g - sleep duration and picture

m4g <- lm(nihtbx_picture_uncorrected.2_year_follow_up_y_arm_1 ~ sleepdisturb1_p.baseline_year_1_arm_1 + nihtbx_picture_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m4g)
confint(m4g)
lm.beta(m4g)

md4g <- modelDiagnostics(m4g, ev.perc = .005)
plot(md4g, ncol = 2, ask = FALSE)

## Model 4h - sleep initiation and picture

m4h <- lm(nihtbx_picture_uncorrected.2_year_follow_up_y_arm_1 ~ sleepdisturb2_p.baseline_year_1_arm_1 + nihtbx_picture_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m4h)
confint(m4h)
lm.beta(m4h)

md4h <- modelDiagnostics(m4h, ev.perc = .005)
plot(md4h, ncol = 2, ask = FALSE)

## Model 4i - both and picture

m4i <- lm(nihtbx_picture_uncorrected.2_year_follow_up_y_arm_1 ~ sleepdisturb1_p.baseline_year_1_arm_1 + sleepdisturb2_p.baseline_year_1_arm_1 + nihtbx_picture_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m4i)
```

## Model 5 - activities
lmer(FCFwavethree ~ activitiesbaseline + FCFbaseline)
## Flanker
```{r}
## Model 5a - art and flanker

m5a <- lm(nihtbx_flanker_uncorrected.2_year_follow_up_y_arm_1 ~ TotalArt.baseline_year_1_arm_1 + nihtbx_flanker_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m5a)
confint(m5a)
lm.beta(m5a)

md5a <- modelDiagnostics(m5a, ev.perc = .005)
plot(md5a, ncol = 2, ask = FALSE)

## Model 5b - sport and flanker

m5b <- lm(nihtbx_flanker_uncorrected.2_year_follow_up_y_arm_1 ~ TotalSport.baseline_year_1_arm_1 + nihtbx_flanker_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m5b)
confint(m5b)
lm.beta(m5b)


## Model 5c - total and flanker

m5c <- lm(nihtbx_flanker_uncorrected.2_year_follow_up_y_arm_1 ~ TotalParticipation.baseline_year_1_arm_1 + nihtbx_flanker_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m5c)
confint(m5c)
lm.beta(m5c)

md5c <- modelDiagnostics(m5c, ev.perc = .005)
plot(md5c, ncol = 2, ask = FALSE)
```
## Pattern Comparison 
```{r}
## Model 5d - art and pattern

m5d <- lm(nihtbx_pattern_uncorrected.2_year_follow_up_y_arm_1 ~ TotalArt.baseline_year_1_arm_1 + nihtbx_pattern_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m5d)
confint(m5d)
lm.beta(m5d)

## Model 5e - sport and pattern

m5e <- lm(nihtbx_pattern_uncorrected.2_year_follow_up_y_arm_1 ~ TotalSport.baseline_year_1_arm_1 + nihtbx_pattern_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m5e)
confint(m5e)
lm.beta(m5e)

## Model 5f - total and pattern

m5f <- lm(nihtbx_pattern_uncorrected.2_year_follow_up_y_arm_1 ~ TotalParticipation.baseline_year_1_arm_1 + nihtbx_pattern_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m5f)
confint(m5f)
lm.beta(m5f)

md5f <- modelDiagnostics(m5f, ev.perc = .005)
plot(md5f, ncol = 2, ask = FALSE)

```
## Picture Sequence
```{r}
## Model 5g - art and picture

m5g <- lm(nihtbx_picture_uncorrected.2_year_follow_up_y_arm_1 ~ TotalArt.baseline_year_1_arm_1 + nihtbx_picture_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m5g)
confint(m5g)
lm.beta(m5g)

## Model 5h - sport and picture

m5h <- lm(nihtbx_picture_uncorrected.2_year_follow_up_y_arm_1 ~ TotalSport.baseline_year_1_arm_1 + nihtbx_picture_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m5h)
confint(m5h)
lm.beta(m5h)

## Model 5i - total and picture

m5i <- lm(nihtbx_picture_uncorrected.2_year_follow_up_y_arm_1 ~ TotalParticipation.baseline_year_1_arm_1 + nihtbx_picture_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m5i)
confint(m5i)
lm.beta(m5i)

md5i <- modelDiagnostics(m5i, ev.perc = .005)
plot(md5i, ncol = 2, ask = FALSE)
```
## Model 6 - screen time
lmer(FCFwavethree ~ screenbaseline + FCFbaseline)
## Flanker
```{r}
## Model 6a - weekday and flanker

m6a <- lm(nihtbx_flanker_uncorrected.2_year_follow_up_y_arm_1 ~ logtotal_weekday1.baseline_year_1_arm_1 + nihtbx_flanker_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m6a)
confint(m6a)
lm.beta(m6a)

## Model 6b - weekend and flanker

m6b <- lm(nihtbx_flanker_uncorrected.2_year_follow_up_y_arm_1 ~ logtotal_weekend1.baseline_year_1_arm_1 + nihtbx_flanker_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m6b)
confint(m6b)
lm.beta(m6b)


## Model 6c - total and flanker

m6c <- lm(nihtbx_flanker_uncorrected.2_year_follow_up_y_arm_1 ~ logtotal_screen1.baseline_year_1_arm_1 + nihtbx_flanker_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m6c)
confint(m6c)
lm.beta(m6c)

md6c <- modelDiagnostics(m6c, ev.perc = .005)
plot(md6c, ncol = 2, ask = FALSE)

# all activities model

mfball <- lm(nihtbx_flanker_uncorrected.2_year_follow_up_y_arm_1 ~ logtotal_screen1.baseline_year_1_arm_1 + TotalParticipation.baseline_year_1_arm_1 + sleepdisturb1_p.baseline_year_1_arm_1 +nihtbx_flanker_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(mfball)
confint(mfball)
lm.beta(mfball)

mdfball <- modelDiagnostics(mfball, ev.perc = .005)
plot(mdfball, ncol = 2, ask = FALSE)

#adjusting for multiple comparisons. holm method
pvflanker <- c(1.11e-12, 0.88, 1.87e-08, 0.000985, 2.53e-08, 1.25e-11, 4.74e-06, 8.13e-10, 6.21e-05, 0.00061, 1.54e-07, 0.0387)

p.adjust(pvflanker, method = "holm")
format(7.740e-02, scientific =FALSE)
```
## Pattern Comparison 
```{r}
## Model 6d - weekday and pattern

m6d <- lm(nihtbx_pattern_uncorrected.2_year_follow_up_y_arm_1 ~ logtotal_weekday1.baseline_year_1_arm_1 + nihtbx_pattern_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m6d)
confint(m6d)
lm.beta(m6d)

## Model 6e - weekend and pattern

m6e <- lm(nihtbx_pattern_uncorrected.2_year_follow_up_y_arm_1 ~ logtotal_weekend1.baseline_year_1_arm_1 + nihtbx_pattern_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m6e)
confint(m6e)
lm.beta(m6e)

## Model 6f - total and pattern

m6f <- lm(nihtbx_pattern_uncorrected.2_year_follow_up_y_arm_1 ~ logtotal_screen1.baseline_year_1_arm_1 + nihtbx_pattern_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m6f)
confint(m6f)
lm.beta(m6f)

md6f <- modelDiagnostics(m6f, ev.perc = .005)
plot(md6f, ncol = 2, ask = FALSE)

#model with all

mpab <- lm(nihtbx_pattern_uncorrected.2_year_follow_up_y_arm_1 ~ logtotal_screen1.baseline_year_1_arm_1 + sleepdisturb1_p.baseline_year_1_arm_1 + TotalParticipation.baseline_year_1_arm_1 + nihtbx_pattern_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(mpab)
confint(mpab)
lm.beta(mpab)

mdpab <- modelDiagnostics(mpab, ev.perc = .005)
plot(mdpab, ncol = 2, ask = FALSE)

#adjusting for multiple comparisons. holm method
pvpattern <- c(0.00699, 0.754 , 9e-07,  0.0464, 1.86e-05, 8.41e-08, 1.09e-05, 1.07e-07, 2.34e-05 , 0.34077, 0.00271)

p.adjust(pvpattern, method = "holm")
```
## Picture Sequence
```{r}
## Model 6g - weekday and picture

m6g <- lm(nihtbx_picture_uncorrected.2_year_follow_up_y_arm_1 ~ logtotal_weekday1.baseline_year_1_arm_1 + nihtbx_picture_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m6g)
confint(m6g)
lm.beta(m6g)

## Model 6h - weekend and picture

m6h <- lm(nihtbx_picture_uncorrected.2_year_follow_up_y_arm_1 ~ logtotal_weekend1.baseline_year_1_arm_1 + nihtbx_picture_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m6h)
confint(m6h)
lm.beta(m6h)

## Model 6i - total and picture

m6i <- lm(nihtbx_picture_uncorrected.2_year_follow_up_y_arm_1 ~ logtotal_screen1.baseline_year_1_arm_1  + nihtbx_picture_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m6i)
confint(m6i)
lm.beta(m6i)

md6i <- modelDiagnostics(m6i, ev.perc = .005)
plot(md6i, ncol = 2, ask = FALSE)

# model with all
mpib <- lm(nihtbx_picture_uncorrected.2_year_follow_up_y_arm_1 ~ logtotal_screen1.baseline_year_1_arm_1 + sleepdisturb1_p.baseline_year_1_arm_1 + TotalParticipation.baseline_year_1_arm_1 + nihtbx_picture_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(mpib)
confint(mpib)
lm.beta(mpib)

mdpib <- modelDiagnostics(mpib, ev.perc = .005)
plot(mdpib, ncol = 2, ask = FALSE)

#adjusting for multiple comparisons. holm method
pvpicture <- c(3.24e-09, 0.429, 3.86e-14, 2e-09, 2e-16, 9.19e-11, 1.96e-06, 2e-09, 0.000328, 0.000232, 1.34e-11)

p.adjust(pvpicture, method = "holm")

```
#Aim 2

#Hypothesis 2A
```{r}
## Model 7a - sleep duration and CT
m7a <- lm(nihtbx_flanker_uncorrected.2_year_follow_up_y_arm_1 ~ sleepdisturb1_p.baseline_year_1_arm_1 + nihtbx_flanker_uncorrected.baseline_year_1_arm_1, data = widedata)

summary(m4a)
confint(m4a)
lm.beta(m4a)
```
# Aim 3

